A performance comparison of Dask and Apache Spark for data-intensive neuroimaging pipelines

### 2019-07-29 latex/paper.tex
Fixed comment in Acknowledgments

Mathieu Dugr\'e was funded by an Undergraduate Student Research Assistant award from
the National Science and Engineering Research Council of Canada. We warmly thank
Compute Canada and \TG{Westgrid?} for providing the cloud infrastructure used in
these experiments, and the McGill Center for Integrative Neuroscience for giving us
access to their cloud allocation.

>>>>

Mathieu Dugr\'e was funded by an Undergraduate Student Research Assistant award from
the National Science and Engineering Research Council of Canada. We warmly thank
Compute Canada and its regional center Westgrid for providing the cloud infrastructure used in
these experiments, and the McGill Center for Integrative Neuroscience for giving us
access to their cloud allocation.
